---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MetabolomicsBasics

<!-- badges: start -->
[![R-CMD-check](https://github.com/janlisec/MetabolomicsBasics/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/janlisec/MetabolomicsBasics/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/MetabolomicsBasics)](https://CRAN.R-project.org/package=MetabolomicsBasics)
<!-- badges: end -->

The goal of MetabolomicsBasics is to provide a set of functions to investigate 
raw data (a matrix of intensity values) from (metabol)omics experiments, i.e. 
following peak picking and signal deconvolution. 
Functions can be used to *i.e.*:

- normalize data
- detect biomarkers
- perform sample classification

A detailed description of best practice usage may be found in 
the publication <https://link.springer.com/protocol/10.1007/978-1-4939-7819-9_20>.

## Installation

You can install the development version of MetabolomicsBasics from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("janlisec/MetabolomicsBasics")
```

## Examples

A typical use case would be to compute a Principal Component Analysis:

```{r example1, out.width="100%", fig.asp=1}
raw <- MetabolomicsBasics::raw
sam <- MetabolomicsBasics::sam
MetabolomicsBasics::RestrictedPCA(dat = raw, sam = sam, group.col = "Group", legend.x = "bottomleft", medsd = TRUE, fmod = "Group")
```
More elaborate plots, like the polar coordinate visualization of heterosis pattern are possible:

```{r example2, out.width="100%", fig.asp=1}
x <- t(raw)
colnames(x) <- sam$GT
MetabolomicsBasics::PolarCoordHeterPlot(x=x, gt=c("B73","B73xMo17","Mo17"), plot_lab="graph", col=1:10, thr=0.5, rev_log=exp(1))
```

